Testing some bootstrap process

### 2024-07-31 test_boot_short_3.Rmd
Another test for better bootstrap variance

---
title: "Testing bootstrap processes"
output: pdf_document
date: "2024-07-30"
---

@@

@@

for (l in 0:((1000/c_dim)-1)) {
  if (l==0){
    x_init <- i*c_dim
  }else if ((3*l+i)*c_dim < (10)*c_dim){
    x_init <- (3*l+i)*c_dim
  }else{
    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
  }
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    h <- nrow(random_points)%%100 # 100 strata
    random_points <- rbind(random_points, list(a,b, h))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y", "Stratum")
return(random_points)
}
```

@@

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-100))
  for (b in 1:B) {
    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
    # (H-1) strata at random
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in unique(df_sample[,3])){
      truc <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
      muche <- mapply(function(RRRRR){df_sample[rownames(df_sample) == RRRRR,]}, truc)
      sample_b <- rbind(sample_b, t(muche))
      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 5)
}
```

>>>>

---
title: "Testing some bootstrap process"
output: pdf_document
date: "2024-07-31"
---

@@

Idea for the bootstrap: for each line l, containing $n_l$ sampled points, $n_l - 1$ points are sampled with replacement. As a result, $100(n_l-1)$ points are sampled from the initial sample. In this case, 900 points are sampled.

@@

for (l in 0:((1000/c_dim)-1)) {
  if (l==0){
    x_init <- i*c_dim
  }else if ((3*l+i)*c_dim < (10)*c_dim){
    x_init <- (3*l+i)*c_dim
  }else{
    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
  }
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    h <- l # 100 lines = 100 strata
    random_points <- rbind(random_points, list(a,b, h))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y", "Stratum")
return(random_points)
}
```

@@

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-100))
  for (b in 1:B) {
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in unique(df_sample[,3])){
      names_h <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
      sample_h <- mapply(function(some_names){df_sample[rownames(df_sample) == some_names,]}, names_h)
      sample_b <- rbind(sample_b, t(sample_h))
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of 5 variables
}
```
